---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# seglm

The goal of seglm is to do a *segmented* regression. Segmented regression, also called *threshold* regression, 
estimates a piecewise linear regression. That is, it estimates a linear regression over multiples segments/regime. Location of the breapoints (aka thresholds) separating each segment is estimated simultaneously. 

When the threshold variable is time, the model reduces to the well-known structural break/changepoint model. 

## Installation


``` r
devtools::install_github("MatthieuStigler/seglm")
```

## Example

The main function is `seglm()`, which uses the standard formula - data style, and specific arguments `th_var_name` and `nthresh`, indicating wich is the threshold variable, as well as how many thresholds/breaks are to be estimated. 

```{r}
library(seglm)

## data randomly generated: true breakpoint is 0 
data_thresh <- sim_thresh()
seglm_lm(formula = y~x, data = data_thresh, th_var = "x", nthresh =1)

```

